Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-03-08 size_differentiated_export.tex
Updates from Overleaf

\section{Results}
\label{sec: Results}
\subsection{\fixme{Seasonal change in dynamical regime? or seasonal cycle in submesoscale activity?}}

@@

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

@@

Time series of particle fluxes in \textit{Papa\_winter} present major differences. In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation. Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}. About 5\% of particles sinking at 0.025 m/day are exported within the first 28 days of the experiment. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features, such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring at submesoscales.

%Time series of exported particles in \textit{Papa\_winter} present major differences. In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking. This earlier arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation. Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}. About 5\% of particles sinking at 0.025 m/day are exported. However, particle export is now stretched over longer periods of time due to particle resuspension. This can be seen in the gentler slopes of the export curves observed in \textit{Papa\_winter} than in \textit{Papa\_summer}.

Particles released in \textit{Papa\_winter} are thus exported faster and in greater numbers than expected from gravitational sinking. Eventually, all sinking particles would be exported in both \textit{Papa\_summer} and \textit{Papa\_winter}, if particles were tracked for a long enough period of time.

\fixme{Here Fig6b should be included an described. The key points are (1) the large difference between velocity class that have $w_s\ll w_{adv}$, and the one that have $w_s\sim w_{adv}$, (2) despite the large difference in \% of particles exported the biomass fluxes are of the same order of magnitude when $\xi=4$ as it is often reported in the ocean, and (3) the predictible decrease in biomass export flux when changing the slope based on equation (8). }

\begin{equation}
    \frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
\end{equation}

\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum})}
	\label{fig: biomass_export}
\end{figure}

@@

The presence of submesoscale dynamics therefore hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass per particle (Figure \ref{fig: sinking_velocity_spectrum}). While the normalized particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

%FIG7
 \begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi =4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\label{fig: biomass_export_remin}
\end{figure}

@@

 Including remineralization of particles (see Equation (\ref{eq: remin_scheme})) significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles slow down as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is considered.

 The total amount of biomass is also reduced compared to the case with no remineralization. The difference is time dependent, and increases with the age of the particle, as particles further remineralize. In a gravitationally-driven system such as during the summer in the northeast Pacific, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases. In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export, with slower-sinking particles contributing significantly less than faster-sinking particles (dash lines in Figure \ref{fig: biomass_export_remin}. Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by 5-6 orders of magnitude depending on the slope of the biomass spectra (see Figure \ref{fig: sinking_velocity_spectrum}). Similar to the case with no remineralization, a change in the Junge slope impacts the biomass contribution of slower-sinking velocity classes. This can be seen in the amount of biomass exported by the 1 m/day sinking-velocity class: A negative slope (i.e., $\xi$ = 4) leads to a maximum biomass of about 6 normalized biomass units \fixme{n.b.u. ?}, while a positive slope (i.e., $\xi$ = 2) leads to a maximum biomass of 1 normalized biomass unit. However, both these contributions to biomass export represent much less than 1\% of the biomass export of the 5 m/day sinking-velocity class, making the contribution to export from the 1 m/day sinking-velocity class virtually insignificant, regardless of the Junge slope.

 In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities. The difference in exported biomass between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported. As particles age, remineralization has an increasing impact and the difference in total exported biomass increases at a rate controlled by the remineralization rate in (\ref{eq: remin_scheme}). Similar to \textit{Papa\_summer}, the total amount of biomass exported by a sinking-velocity class decreases as the Junge slope decreases (i.e., the sinking-velocity spectra flattens). %An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the amount of biomass exported from the 0.025 m/day sinking-velocity class exceeds the amount of biomass exported by both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.

@@

\subsection{Physical model}
\label{sec: Discussion_model}
\textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the northeast Pacific Ocean. After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observations from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}). The two experiments, however, show significantly different distributions of $M^2$, with the winter distribution exhibiting a longer tail, suggesting sharper density gradients. The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.

@@

The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa by shortening the export timescale of particulate matter. The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion below). However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}. Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior. In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles.

@@

Analyses of particle tracking experiments reveal that the role played by slower\-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope coefficient $\xi$).

Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer. In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer. This change in dynamics has a clear impact on the amount of particles exported for all sinking-velocity classes modeled in this experiment.

Particles within a sinking-velocity class are exported both more rapidly and over longer timescales. In fact, a portion of the particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics. This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale. The former evidently needs to be shorter than the latter to efficiently export POC. However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported more gradually in time. This is due to upward vertical currents, re-suspending material that would otherwise sink, and thus delay its export.

In the summer, the gravitationally-driven export mechanism efficiently exports faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles. In the winter, however, the export mechanisms is advectively-driven, which leads to a smaller export of faster-sinking particles than in the summer due to resuspension, but efficiently exports slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: sinking_velocity_spectrum}). These two competing mechanisms rise the questions as to which process is most efficient in exporting particulate material below the winter mixed layer.

%% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient. Over the course of our simulation, the total amount of biomass exported is consistently enhanced when $\xi = 4$ (10 to 60\% increase) in the presence of submesoscale dynamics. For a flat biomass spectrum ($\xi = 3$), the export enhancement due to submesoscale dynamics is always smaller than 20\%.\fixme{eventually all is exported...} When $\xi =2$, the amount of biomass exported in the presence of submesoscale dynamics varies between 95 and 110\% of the export observed in the summer, when submesoscale dynamics are not active. Therefore, to address the questions formulated above, export is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales. %Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})? Showing stronger, more localized downwelling, and broader and weaker upwelling?

\fixme{modify when results section is edited}
Introducing remineralization processes significantly decreases the total amount of biomass exported. Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export. The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increases with larger $\xi$. Total exported biomass almost doubles when $\xi =4$, and increases by 5 and 20\% for $\xi =2$ and $\xi = 3$, respectively. This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to slow these particles down and thus prolongs their export timescales. In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as all classes rely on gravitational sinking for export. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics, leading to a greater net export than when remineralization is not considered.

@@

In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$). Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}. Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}). Because of the negative slope in the biomass spectrum, any particle class sinking at a faster rate will not contribute as much to the biomass export. The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth. As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})). A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}). Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon} towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.

@@

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}). In this regime, slower-sinking particles significantly contribute to POC export. In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$. Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller in advectively-driven export mechanism, as opposed to gravitationally-driven.

>>>>

\section{Results}
\label{sec: Results}
\subsection{Seasonal dynamical regimes}

@@

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of particle export flux closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

@@

Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b). In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward export within the first 15 days of the simulation. For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring at submesoscales. %\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}

The biomass export fluxes computed from the particle flux shown in Figure \ref{fig: particle_export} using two different Junge slopes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b). The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$). However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model (Figure \ref{fig: particle_export}), suggesting that the export for this sinking-velocity class tend to be gravitationally-driven.

\begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}). Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
	\label{fig: biomass_export}
\end{figure}

As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics. Figure \ref{fig: biomass_export} shows the biomass export fluxes in normalized units for two different Junge slopes. The contribution from slow-sinking particles to the total biomass export flux expectedly decreases with the Junge slope. The decrease in biomass export flux is constant through time and can be predicted using Equation (\ref{eq: biomassjungeslope}):

\begin{equation}
    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_s_0}\right)^{\frac{\xi_2-\xi_1}{2}}
    %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
\end{equation}
Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively. %\fixme{The evolution of the biological community through time that would affect the slope of the size spectrum also has direct consequences on the export of the slower-sinking particles.}

The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}). While the normalized particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

@@

@@

 Including remineralization of particles (see Equation (\ref{eq: remin_scheme})) significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles slow down as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.

 %FIG7
 \begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\label{fig: biomass_export_remin}
\end{figure}

 The biomass export flux is also reduced compared to the case with no remineralization. In a gravitationally-driven system such as during the summer in the northeast Pacific, captured in \textit{Papa\_summer}, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases. In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export over different timescales (dash lines in Figure \ref{fig: biomass_export_remin}). Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by several orders of magnitude.

 In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}. The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported. As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}). An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.

@@

\subsection{Dynamical Regimes}
\label{sec: Discussion_model}
\textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the northeast Pacific Ocean. After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observations from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}). The two experiments, however, show significantly different distributions of $M^2$, with the winter distribution exhibiting a longer tail, suggesting sharper density gradients. The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.

@@

The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa by shortening the export timescale of particulate matter. The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion in Section \ref{sec: discussion_particle}). However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}. Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior. In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles and thus exclude part of the particle spectrum from contributing to the export flux.

@@

Analyses of particle tracking experiments reveal that the role played by slower-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).

Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer. In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer. This change in dynamics has a clear impact on the export flux of all sinking-velocity classes modeled in this experiment. Particle export within a sinking-velocity class is hastened and occur over longer timescales. In fact, particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics. This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale.; The former evidently needing to be shorter than the latter to efficiently export POC. However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported over longer timescales. This is due to upward vertical currents, re-suspending material that would otherwise sink, and thus delay its export (Figure \ref{fig: particle_export}).

In the summer, the gravitationally-driven export mechanism efficiently exports faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles. In the winter, however, the export mechanisms is advectively-driven, which leads to a slightly weaker export flux of faster-sinking particles than in the summer due to resuspension, but a much larger export flux of slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: biomass_export}). These two competing mechanisms raise the question as to which process is most efficient in exporting particulate material below the winter mixed layer.

%% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient (Figure \ref{fig: biomass_export}). Over the course of our simulation, the biomass export flux is consistently enhanced when $\xi = 4$ in the presence of submesoscale dynamics. Therefore, export flux is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales. %Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})? Showing stronger, more localized downwelling, and broader and weaker upwelling?

Introducing remineralization processes significantly decreases the biomass export flux. Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export. The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increases with larger Junge slopes. This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to slow these particles down and thus prolongs their export timescales. In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as all modeled classes rely on gravitational sinking for export. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics, leading to a greater net export flux than when remineralization is not considered.

@@

In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$). Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}. Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}a). Because of the negative slope in the biomass spectrum, any particle class sinking at a faster rate will not contribute as much to the biomass export. The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth. As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})). A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}a). Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.

@@

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b). In this regime, slower-sinking particles significantly contribute to POC export. In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$. Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.
